\documentclass{report}
\usepackage[tmargin=2cm, rmargin=1in, lmargin=1in,margin=0.85in,bmargin=2cm,footskip=.2in]{geometry}
\usepackage{amsmath,amsfonts,amsthm,amssymb,mathtools}
\usepackage{enumitem}
\usepackage[]{mdframed}
\usepackage{tikz}
\usepackage{minibox}
\renewcommand{\familydefault}{\sfdefault}

\title{\Huge{Art 25}}
\author{\huge{Elijah Hantman}}
\date{}

\begin{document}
\maketitle
\newpage

{\huge Navigating The American Spectacle}

\begin{description}
    \item {\large Pre Class}
        \begin{mdframed}
            Goal is to build a bridge from traditional art mediums
            to games and ludic play.
            \begin{center}
                \minibox[frame]{
                    Note: If something is needed
                    before class try and email him.
                    Better to ask after class if possible.
                }
            \end{center}
        \end{mdframed}
        \begin{mdframed}
            Fire in Los Angeles, loss of art, homes,
            memories. 
        \end{mdframed}
    \item {\large Action 1}
        \begin{mdframed}
            Aesthetics vs Art
            \begin{itemize}
                \item Aesthetics is the study of perception,
                    how things look, taste, smell, sound, etc.
                    How things are brought together, to form
                    concepts like disaster, love, etc. A study
                    of How we experience the world.
            \end{itemize}
        \end{mdframed}
        \begin{center}
            \minibox[frame]{
                I don't like this lecture style.\\
                Jargon and terminology is used without\\
                care or craft. Everything is unstructured\\
                and its a morass of ideas. I fail to see\\
                the artistry of this lecture.
            }
        \end{center}
        \begin{itemize}
            \item He is quoting Duchamp in his worries about
                artists which change things disappearing.
                I don't really like this, there is artistry
                in mastery. And I think it is elitist to designate
                some painters as not artists.
            \item Oh god he's talking about the Matrix now.
            \item His software analogies make me depressed.
                I wish he would please stop.
            \item I dislike how he will make analogies between
                software and our selves without care or
                clarity. He seems to be reaching for a
                picture of self in which we construct our
                selves piece by piece like an engineer
                carefully constructing a bridge, sourcing
                materials from our surroundings and societal
                context.
            \item The talk about imaginative or social
                play is kinda cool, but its kinda
                mainstreamy.
            \item Ludus is how play is structured
            \item Paidia is how play happens in a structure
        \end{itemize}
    \item {\large}
    \item {\large}
\end{description}




\end{document}
