\documentclass{report}
\usepackage[tmargin=2cm, rmargin=1in, lmargin=1in,margin=0.85in,bmargin=2cm,footskip=.2in]{geometry}
\usepackage{amsmath,amsfonts,amsthm,amssymb,mathtools}
\usepackage{enumitem}
\usepackage[]{mdframed}
\usepackage{tikz}

\title{\Huge{Math 181}}
\author{\huge{Elijah Hantman}}
\date{}

\begin{document}
\maketitle
\newpage

\begin{description}
    \item Course Details 
        \begin{mdframed}
            Instructor: Jesse Leo Kass\\
            Instructor Email: jelkass@ucsc.edu\\
            Office Hours: MWF 3:05pm - 4:00pm in McHenry 4174

            Prefer address as Jesse, email is for specific
            issues, Canvas Course Feedback is for annonymous
            messages, and Office hours are best for math
            help.
        \end{mdframed}
        \begin{mdframed}
            {\large Textbooks}\\
            Required!!!
            \begin{enumerate}
                \item Katz, Victor. A History of Mathematics 4 ed.
                \item Wardhaugh, Benjamin. How to Read Historical
                    Mathematics
                \item Netz, Reviel and Noel, William
                    The Archimedes Codex.
                \item Stedall, Jacqueline. The History of
                    Mathematics: A Very Short Introduction
            \end{enumerate}
        \end{mdframed}
        \begin{mdframed}
            {\large Grading}\\
            Entirely based on homework, final exam, and
            final paper. Grade breakdown is:
            \begin{itemize}
                \item Final Paper 20\%
                \item Final Exam 30\%
                \item Homework 50\%
            \end{itemize}
        \end{mdframed}
        \begin{mdframed}
            {\large Homework}
            \begin{itemize}
                \item Collected on a Weekly Basis
                \item I think it is all printed or written
                    out
                \item If you miss a lecture put homework in his
                    mailbox at McHenry before class.
                \item A one paragraph description of all resources
                    used is required with each homework. Any person,
                    book, etc. must be mentioned.
                \item As long as it is clear you did as much as you could
                    and was honest and clear about what you did there
                    will be no academic misconduct.
            \end{itemize}
        \end{mdframed}
        \begin{mdframed}
            {\large Misc}
            \begin{itemize}
                \item Silent phone
                \item Inform before showing up late
                \item Inform before leaving early
            \end{itemize}
        \end{mdframed}


    \item What is History of Mathematics?
        \begin{mdframed}
            \begin{itemize}
                \item Older academic works paint math as a
                    primarily European endeavor with other
                    peoples being primitive
                \item This is reductive and not what the
                    goal of this class is 
                \item Goal is to understand a larger more
                    comprehensive view of math that is inclusive
                    of Women, Indigenous peoples, etc.
            \end{itemize}
        \end{mdframed}
\end{description}


\end{document}
