\documentclass{report}
\usepackage[tmargin=2cm, rmargin=1in, lmargin=1in,margin=0.85in,bmargin=2cm,footskip=.2in]{geometry}
\usepackage{amsmath,amsfonts,amsthm,amssymb,mathtools}
\usepackage{enumitem}
\usepackage[]{mdframed}
\usepackage{tikz}

\title{\Huge{CRES 10}\\Day 10 Notes}
\author{\huge{Elijah Hantman}}
\date{}

\begin{document}
\maketitle
\newpage

\begin{description}
    \item {\large Recap Stuff}
        \begin{itemize}
            \item Emily Pankerst?
            \item Last time
                \begin{itemize}
                    \item Structural vs Short term genocide
                        \begin{mdframed}
                            Structural genocide is a broader
                            systemic and structural movement.
                            Structural genocide is about
                            justifying and normalizing genocide
                            while sudden genocide is the
                            immediate outburst of the desire
                            to kill or annihilate a group.
                            \\
                            Structural genocide also uses
                            cultural, economic, and ethnic
                            appropriation and suppression.
                            Indigenaeity is consumed and
                            assimilated. Living communities
                            are downplayed and sidelined for
                            constructed versions of themselves.
                            \\
                            We are the new natives, taking the
                            legacy of the ancient peoples of
                            this land.
                        \end{mdframed}

                        \begin{mdframed}
                            Structural genocides have caused
                            massive reductions in life
                            expectancy. They are crammed into
                            reservations which are underfunded
                            non-community held, and exploited.

                            Indigenous people are put into
                            no win scenarios where they are
                            trapped into forever debt. The
                            debt becomes leverage to seize
                            all the land.
                        \end{mdframed}
                    \item Law vs Justice
                \end{itemize}
            \item Where did the Cowboy come from?
                \begin{itemize}
                    \item Malborro cigarrettes?
                    \item Real life cattle ranching was
                        mostly done by African Americans,
                        Mexican Americans, and Indigenous
                        people.
                    \item Came from image of Ex-Confederates
                        \begin{mdframed}
                            Noble independence and searching
                            for a cause comes from the
                            fact the confederacy fell.

                            The fetishization of the Cowboy
                            fed into ideas of individualism
                            and rebellion as values.
                        \end{mdframed}
                \end{itemize}

            \item Genocide in Palestine
                \begin{itemize}
                    \item Coverage of Gaza war favors Israel
                        \begin{mdframed}
                            The language used to describe
                            the palestinian genocide dehumanizes
                            and minimizes their deaths.

                            The Passive voice is used to ascribe
                            agency to only one group,
                            Palestinians. Israelis have no
                            choice, their killing of Palestinians
                            is an unfortunate reality, while
                            the killing of Israelis is a
                            tragedy and necessitates the murder
                            of Palestinians.
                        \end{mdframed}
                \end{itemize}
            \item What is the point of the word genocide?
                \begin{mdframed}
                    Genocide has a cultural and moral meaning.
                    We do not need to relinquish the idea
                    of genocide to legislation. We do not
                    need to law to tell us what genocide is
                    or what should be considered genocide.
                \end{mdframed}
                \begin{mdframed}
                    The historical context of the law
                    is impossibly important. All laws
                    are records of the concerns and ideas
                    of the times it was formulated in.
                \end{mdframed}
                \begin{mdframed}
                    All law is made by people, we need not
                    defer to those who do not live in our times
                    or know the world we live in. We can
                    shape and imagine a better world if we
                    want to.
                \end{mdframed}
            \item Emily Pankhurst
                \begin{itemize}
                    \item Started woman's sufferage movement
                    \item arrested multiple times and movement
                        was classified as a terrorist
                        movement.
                        \begin{mdframed}
                            Used slogan "Deeds, not words"
                            and took non-legal means to 
                            change the law.

                            They used civil disobediance and
                            other illegal and extralegal
                            methods to incite change and put
                            pressure. They organized hunger strikes
                            and protests, etc.

                            Openly stated that the point of
                            activism was about making the cost
                            of the status quo so high that
                            to change is compulsory.

                            They burned ballot boxes, attacked
                            politicians, sending letter bombs
                            to politicians, etc.
                        \end{mdframed}
                    \item They succeeded, and were brought into
                        celebrated society. 
                        \begin{mdframed}
                            What does it mean that they fought
                            for the right to be folded into
                            a genocidal empire?

                            They won, but what exactly did they
                            win?
                        \end{mdframed}
                \end{itemize}
        \end{itemize}
    \item {\large Recipe for Property}
        \begin{itemize}
            \item Rights are conceptualized as rights
            \item Whitness is used to create property.
                \begin{itemize}
                    \item Whiteness is a floating signifier
                        \begin{mdframed}
                            Term for a word or idea that can
                            change and take on many different
                            ideas while not being tied to any
                            single idea.

                            Whiteness can be about skin color,
                            intelligence, purity, innocence,
                            deserving, beauty, power, violence,
                            peace, enlightenment, etc.
                        \end{mdframed}
                \end{itemize}
            \item What if Whiteness wasn't property?
                \begin{mdframed}
                    Whiteness would lose its value.
                    Large conflicts between those with
                    lots of property and those with little
                    property. With whiteness ceasing to be
                    a meaningful group, class becomes more
                    important and obvious.
                \end{mdframed}
            \item What if we add Whiteness back in?
                \begin{mdframed}
                   Both workers and owners gain a common
                   identiy. They both own whiteness, and whiteness
                   is an exclusive group with all kinds of good
                   qualities attached.
                \end{mdframed}
                \begin{mdframed}
                    The thing that make whiteness valuable is
                    the enslavement, extraction, and dispossesion
                    of not having whiteness. A well is dug, and
                    the fear of that well gives whiteness its
                    value.
                \end{mdframed}
                \begin{mdframed}
                    To maintain and enforce whiteness you have
                    to go to the upper class. You have to 
                    identify with the system, embrace it,
                    and enforce it.
                \end{mdframed}
            \item Takeaways?
                \begin{itemize}
                    \item Racism allows for lower and upper 
                        classes to feel equal.
                    \item Racism prevents white people from
                        feeling their inequality, racism allows
                        them to leave and exploit and bring
                        whiteness to new places.
                    \item Racism is not so different in economic
                        and social dynamics from class. Racism
                        allows for class to be bridged and
                        ignored.
                \end{itemize}
            \item Racism is a structure
                \begin{itemize}
                    \item scaled up set of social relationships
                    \item Working Class White people are made
                        to be superior, but insecure.

                        The moniker of white can be recinded at
                        any time.
                    \item The one who benefits is the people who
                        gain when people work hard to demonstrate
                        their superiority.
                \end{itemize}
            \item Property comes from the enforcement and 
                reiteration of a multitude of overlapping
                systems and laws.
        \end{itemize}
\end{description}


\end{document}
