\documentclass{report}
\usepackage[tmargin=2cm, rmargin=1in, lmargin=1in,margin=0.85in,bmargin=2cm,footskip=.2in]{geometry}
\usepackage{amsmath,amsfonts,amsthm,amssymb,mathtools}
\usepackage{enumitem}
\usepackage[]{mdframed}
\usepackage{tikz}

\title{\Huge{CRES 10}\\Discussion 2 Notes}
\author{\huge{Elijah Hantman}}
\date{}

\begin{document}
\maketitle
\newpage

\begin{description}
    \item Am I a settler?
        \begin{mdframed}
            I think that I am a settler, but it is something that makes me
            deeply uncomfortable. The area I live in is drenched with
            reminders of the history. Gold country, we went to Sutter's
            Mill as a kid, and I remember learning about all sorts of
            Indigenous tidbits in history class. As I got older I started learning
            about colonialism. First from hearing about oil companies bulldozing and using
            riot police on Native protests. I started learning about massacres
            and war crimes, not really on purpose, but more as an extension
            of my general political understanding.

            My family is perhaps an example of minority execellence. My dad
            was a Jewish kid from a dysfunctional family, and my Mom is
            a first generation immigrant from the Phillipines. I don't
            really feel either of those identities in full honesty,
            but those ideas also led me to see my family, not in the
            context of settlers, in the context of whiteness, but in
            terms of surviving.

            I find in my interests I am inextricably linked to colonialism.
            As a lover of computers, and infrastructure, space travel
            and all the scifi out there I can't help but find myself unable
            to entirely hate the practices of extraction. I don't want them
            to continue, and they are wrong. I think climate change and 
            destructive mining and the like are unsutainable and violent.
            However I can't help but want to imagine a world that is sustainable
            and still has all those things, computers, and cool buildings, and
            so on.

            I think that I am a settler in the same way anyone is when they
            play the game of living in a capitalist society. I have to work
            to survive, and my family moved to gain better opportunities.
            I live on land which was stolen, and live in an economy made
            of the products of violent conquest. 

            Sometimes I feel that I am burnt out on colonialism and
            imperialism, because to contemplate it every day is to
            impose a mental burden that nobody should have to. I am privledged
            enough to shrug off that burden sometimes, but I know Indigenous
            people and POC lack those priledges, and they are forced to not only
            confront those things, but are directly attacked by those things every day.
            Sometimes I feel my mind is not strong enough to hold everything in my
            head.
        \end{mdframed}

    \item {\large Responses}
        \begin{mdframed}
            \begin{itemize}
                \item Not a settler because am an immigrant.

                    setters are "natural"

                \item What is turkish? The state squashes differences
                    between groups via beauocracy and legislation 

                \item The point of view that settler isn't something
                    that you control, so much as you are forcibly
                    part of a society which does colonialism.

                    Slaves are settlers but not willing.

                \item Definitely a Settler, prior generational trauma doesn't absolve
                    participation and entrenchment in colonialism.

                    What can you do with this identity?

                \item OG settlers. Already happened, can't really fault
                    yourself for things you didn't choose. Guilt isn't
                    a necessary part of a settler identity.
            \end{itemize}
        \end{mdframed}

    \item Reading Review
        \begin{mdframed}
            \begin{itemize}
                \item I think that he has an implicit definition of what matters to
                    being a settler. I think given that implicit definition he is
                    practically categorically correct.

                \item System is inescapable. He is quick to attempt to clarify
                    what exactly he means by settler. 

                \item He validates the conflict between being a settler and
                    the desire to not be a settler. 

                \item Easier to accept, the history is bad but you aren't a bad
                    person for existing.

                \item Using indigenous terminology to define himself as a settler.
                    Being a settler is an unfortunate identity, like having a
                    Nazi in the family.

                \item It's not you are entirely complicit in. Agency in the
                    identity is made explicit.

                \item Opposite, settlers can't redefine what it means to be
                    a settler because its more valuable to analyze
                    history from an indigenous perspective.
            \end{itemize}
        \end{mdframed}

    \item Coates The Message
        \begin{itemize} 
            \item Effectively a tourist, which is an extension of settler/colonialism
                
                Settlers in Israel are treated better than Palestinians.

        \end{itemize} 

\end{description}


\end{document}
