\documentclass{report}
\usepackage[tmargin=2cm, rmargin=1in, lmargin=1in,margin=0.85in,bmargin=2cm,footskip=.2in]{geometry}
\usepackage{amsmath,amsfonts,amsthm,amssymb,mathtools}
\usepackage{enumitem}
\usepackage[]{mdframed}
\usepackage{tikz}
\usepackage{minibox}
\renewcommand{\familydefault}{\sfdefault}

\title{\Huge{Art 25}\\Edo Stern}
\author{\huge{Elijah Hantman}}
\date{}

\begin{document}
\maketitle
\newpage

\begin{itemize}
    \item {\large Games}
        \begin{itemize}
            \item Vietnam Romance (film, computer game, performance...)
                \begin{mdframed}
                    Art style was a tough choice. Ended up with a 
                    comic style with the goal of impressionism.
                \end{mdframed}
                \begin{mdframed}
                    Lots of reading and researching. Some heroics,
                    some books about the brutality of the war machine.
                \end{mdframed}
                \begin{mdframed}
                    2D game, with 3d elements, heavily cell shaded, very
                    thick bold outlines.
                \end{mdframed}

                \begin{mdframed}
                    I kinda dislike his setup. He makes games but in a
                    fine arts way. People can't play his game, I can't
                    dissect how it is made or share it. He only lets
                    his games be played in museums and installations
                    on massive screens.

                    He claims it has some phenomenological component,
                    I wonder if the experience of being in a museum,
                    of not being able to take your time with the game
                    takes away from its messaging. His art is also
                    delibrately exclusionary.

                    The game itself is honestly not particularly subtle
                    or nuanced. Its kind a fine but it feels like something
                    which doesn't really benefit from being in a large
                    display.
                \end{mdframed}
            \item Dark Game
                \begin{mdframed}
                    Its kinda cool. The tech is more interesting.
                \end{mdframed}
                \begin{mdframed}
                    Partially inspired by American Taliban, American kidnapping
                    of a kid.
                \end{mdframed}
                \begin{mdframed}
                    Later versions aimed for hearing and vision impaired people.
                    Idea is to make games which are fun for people with vision or
                    hearing impairments.
                \end{mdframed}
                \begin{mdframed}
                    Darkgame 5 plays with senses as a resource and game mechanic.
                \end{mdframed}
            \item Man Versus
                \begin{mdframed}
                   Based on his wife's novel. 
                \end{mdframed}
                \begin{mdframed}
                    Cyberpunk / Feminist
                \end{mdframed}
                \begin{mdframed}
                    Foot fetish lmao, health is based
                    on footwear.
                \end{mdframed}
        \end{itemize}
\end{itemize}


\end{document}
