\documentclass{report}
\usepackage[tmargin=2cm, rmargin=1in, lmargin=1in,margin=0.85in,bmargin=2cm,footskip=.2in]{geometry}
\usepackage{amsmath,amsfonts,amsthm,amssymb,mathtools}
\usepackage{enumitem}
\usepackage[]{mdframed}
\usepackage{tikz}
\usepackage{listings}


\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{c_style}{
    language=C,
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstdefinestyle{asm_style}{
    language=asm,
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}




\title{\Huge{CSE 115A - Introduction to Software Engineering}}
\author{\huge{Elijah Hantman}}
\date{}

\begin{document}
\maketitle
\newpage

What even is Software Engineering?
\begin{mdframed}
    \begin{itemize}
        \item Not Computer Science 
        \item Not just programming 
        \item What makes software different than other mediums?
    \end{itemize}

    It is about Products, process, and creating useful systems.
    It is about the programming and Computer Science, but it is
    also about what and why you are building what you are building,
    as well as how you build it, who you work with, how people contribute,
    how decisions are made, etc.

    Learning Goals
    \begin{itemize}
        \item Design principles
        \item Processes
        \item Development methods
    \end{itemize}
\end{mdframed}

Hierarchy of Changes, planning and Estimates
\begin{itemize}
    \item High level versions
    \item each version contains multiple sprints
    \item Each sprint contains multiple stories
    \item Each story contains multiple tasks to be completed
\end{itemize}

Planning at the low level includes exact implementation
details. At the high level planning includes features,
fixes, api design, etc. At the highest level planning is
about what each 'finished' version of the software will
be.


Release Plan
\begin{mdframed}
    Transfer to customer, and the thing being created.

    Suggestions are collected. The team works to convert
    suggestions into specific tasks and features. Only a portion
    of all suggestions and requests can be fulfilled.
\end{mdframed}

Roles
\begin{mdframed}
    \begin{itemize}
        \item team
            \begin{itemize}
                \item Team
                    No hierarchy here. Developers are supposedly equally
                    empowered to determine how each sprint works. Should
                    only change membership between sprints.

                    Ideally its composed of different people with many different
                    skills.

                \item Product Owner, define features of product, decides
                    on release date and content, responsible for profit,
                    prioritize features, accept or reject results.
                \item SCRUM master

                    represents project management, manages and facilitates SCRUM,
                    works to keep team productive, interface with external management.
            \end{itemize}
    \end{itemize}
\end{mdframed}

Each Sprint is fixed. Change only happens between sprints
or when all developers agree.


Release
\begin{mdframed}
    \begin{itemize}
        \item Determine User Stories to include
            \begin{itemize}
                \item Goal, or thing user wants to do
                \item Analyze concept
                \item decompose into set of stories
                \item prioritize stories
                \item estimate difficulty and time required for each story
                
            \end{itemize}

            Direction of sprint planning process, functional description of
            what the product should be.
    \end{itemize}
    INVEST
    \begin{itemize}
        \item Independent

            Free of implementation dpendencies on other stories
        \item Negotiable

            Must be concrete enough to be debated.

        \item Valuable

            Should be worth the effort

        \item Estimateable

            Possible to estimate order of magnitude or relative
            amount of work

        \item Sized appropriatedly

            Need to fit in a sprint, or be converted into
            tasks which can be finished in a sprint

        \item Testable

            Should be verifiable that the story has been implemented or
            resolved
    \end{itemize}

\end{mdframed}

\end{document}

