\documentclass{report}
\usepackage[tmargin=2cm, rmargin=1in, lmargin=1in,margin=0.85in,bmargin=2cm,footskip=.2in]{geometry}
\usepackage{amsmath,amsfonts,amsthm,amssymb,mathtools}
\usepackage{enumitem}
\usepackage[]{mdframed}
\usepackage{tikz}

\title{\Huge{CRES 10}\\Day 11 Notes}
\author{\huge{Elijah Hantman}}
\date{}

\begin{document}
\maketitle
\newpage
\begin{description}
    \item {\large Recap/Review} 
        \begin{itemize}
            \item Government worker union started in 1970s
                
                Fairly controversial, unionizing is a right
                which is not garunteed and is often removed
                at the whims of the president.

            \item Since 1980s Democrat coalition has been
                formed by compromise. They move right rather
                than building a base on the left and for
                minorities

            \item Current US government is oriented in
                support of a military industrial complex.

            \item The cutting of social services pushes
                people into the military, it made room
                for more funding for war.
        \end{itemize}
    \item {\large The Electoral College}
        \begin{enumerate}
            \item Comes from the first constitutional convention
            \item Who should be represented and how much?
            \item Many framers thought that representation
                should be about personhood and wealth.
            \item Many of the strongest advocates for wealth
                based representation were slaveholders.
            \item Electoral college was made with this in mind.
                Compomised with Senate that was two representatives
                per state, and House with representatives proportional
                to population.
        \end{enumerate}
    \item {\large Recipe For Property}
        \begin{itemize}
            \item Material
                \begin{itemize}
                    \item Land
                    \item Labor
                    \item "Natural" Resources
                    \item Social relations
                \end{itemize}
            \item Discursive
                \begin{itemize}
                    \item Freedom / Unfreedom
                    \item Civilized / Savage distinction
                    \item Deserving / Undeserving
                    \item Entitlement / inhabitation
                    \item etc.
                \end{itemize}
            \item Institutional
                \begin{itemize}
                    \item Military
                    \item Religious
                    \item Science / knowledge making
                    \item Media
                    \item Workplaces
                    \item Families / kinship
                \end{itemize}
        \end{itemize}
        This narrative of property is not exclusive to
        White people. The promise of whiteness, of power, of
        property is embedded in everyone. Even if they might
        never be fully white, they can strive to remake themselves
        as white-er. You can be a little like the white folk, ie:
        have property, wealth, political power, innocence, etc.
    \item {\large }
\end{description}



\end{document}
