\documentclass{report}
\usepackage[tmargin=2cm, rmargin=1in, lmargin=1in,margin=0.85in,bmargin=2cm,footskip=.2in]{geometry}
\usepackage{amsmath,amsfonts,amsthm,amssymb,mathtools}
\usepackage{enumitem}
\usepackage[]{mdframed}
\usepackage{tikz}

\title{\Huge{CRES 10}\\Day 13 Notes}
\author{\huge{Elijah Hantman}}
\date{}

\begin{document}
\maketitle
\newpage

\begin{description}
    \item {\large Announcements} 
        \begin{itemize}
            \item Monakea Protectors -> orientation Friday
        \end{itemize}

    \item {\large Election} 
        \begin{itemize}
            \item Trump won
            \item Trump won the popular vote
            \item Also Republicans won congress
            \item Other's thoughts
                \begin{itemize}
                    \item Project 2025, far right plan
                        associated with Donald Trump
                        \begin{itemize}
                            \item Kicking out undocmented immigrants
                            \item Who would be kicked out?
                            \item What about visa holders?
                            \item Ran on mass deportation,
                                unknown how it will be
                                implemented, if at all.
                            \item States can fight back,
                                and some will.
                            \item Its a bad times to be
                                a non-citizen.
                        \end{itemize}
                    \item Project 2025 bad for economy?
                        \begin{itemize}
                            \item Would there be bad repercussions
                                for mass deportations?
                            \item Yes. Kinda obvious, immigrants
                                are both scape goats and a key
                                place where value is extracted
                                from.
                            \item Unlikely to be legislated,
                                likely to be continuation of
                                Biden's and Obama's policy.
                            \item Shit is real and is real bad.
                        \end{itemize}
                    \item Did Kamala's choice to try and appeal
                        to right wing voters lose her the
                        election?
                        \begin{itemize}
                            \item Harris tried to win over
                                the Nicky Haley faction.
                            \item One of the significant reasons
                                Harris lost.
                            \item Harris tried to recruit
                                old Bush-era republicans.
                            \item The strategy of prying away
                                voters from an opponent was only
                                really successful in a couple
                                campaigns. Obama to a lesser
                                degree, and Ronald Reagan.
                            \item To be Reagan you have to
                                have the 60s as a background,
                                be a white conservative man
                                and do a little bit of Racism.
                        \end{itemize}

                    \item What happened to the Blue wall?
                        \begin{itemize}
                            \item Inflation is racialized
                            \item Inflation makes people look
                                for an explanation, so by
                                giving an explanation, even
                                a nonsensical one, you can
                                mobilize a lot of people.
                            \item Republicans have a lot of
                                explanations,

                                \begin{itemize}
                                    \item Stimulus going to
                                        undeserving
                                    \item Racism
                                    \item Black people on welfare
                                    \item etc.
                                \end{itemize}
                        \end{itemize}
                    \item Some mainstream rhetoric has been
                        attributing Democrat loss is Democrats
                        being too "Liberal", and running on
                        cultural ideas. Also rampant college
                        students being activists on college
                        campuses. On campus, new time, place, manner 
                        requirements are being put in place
                        for protesters. Police officers already
                        have arrested a student.
                \end{itemize}
            \item Trump has suggested he will close department
                of Education.
                \begin{itemize}
                    \item Part of Presidential cabinet, and
                        is supposed to execute education policy.
                        The President is able to staff these
                        departments so has outsized influence.
                    \item Part of the purview of the Department
                        of Education is University grants, funding
                        and student loans. By threatening or directly
                        cutting funding the Department of Education
                        has the ability to cripple a University.
                    \item Unlikely to close the Department of Education,
                        Republicans have kids too, but also it is
                        a massive source of leverage for himself.
                \end{itemize}
            \item Did Trump win because he was the prefferred candidate?
                Or were people voting against Kamala?
                \begin{itemize}
                    \item Who knows? The data is still new and not yet
                        throughly analyzed.
                    \item Current guess is that Harris has low voter
                        turnout. Many didn't care, and many didn't
                        trust her competence.
                    \item Harris lacked time to build trust, and she
                        is a Black woman who is automatically at a
                        disadvantage. Some of the people not seeing
                        her as competent did so due to misogyny and
                        racism.
                    \item Harris didn't distinguish herself. She had
                        no clear central campaign message apart from
                        "I'm not Trump".
                    \item Latino men shifted towards Trump, felons voted
                        for Trump. Lots of weird racist hand wringing
                        early in the campaign which never ended up
                        panning out.
                    \item Many reasons for Kamala's loss.
                \end{itemize}
            \item Election as a battle for the sexes. Harris had only
                3 months to campaign. Harris was unable to cater to
                the male vote? America may not be progressive enough
                to elect a woman.
                \begin{itemize}
                    \item Unclear why things happened as it did.
                    \item Harris had a lot of status quo support,
                        still outspent.
                    \item Not certain that Harris' loss was due to
                        being a Black Woman.
                    \item Side note: The US doesn't really care
                        for being a progressive nation. US is fairly
                        proud of being, conservative.
                \end{itemize}
            \item What will be different this Trump term?
                \begin{itemize}
                    \item I don't know.
                    \item The future is unknown
                    \item First term was a shock so he got more
                        pushback. Now it is a turning point, who
                        knows how?
                    \item Some see it as a disintigration of US
                        empire, but who knows?
                    \item US militarism and empire will not lose any
                        steam with Trump. He is fully in favor of
                        both according to all evidence.
                    \item The revelation of the past year and a half
                        has shown that the US is indifferent to
                        evidence, protest, public opinion, etc.
                    \item The US has not for a long time relied on
                        the consent of anybody. 
                    \item Whatever the US is, it is far from a
                        Democracy, and we can not analyze it in
                        that frame.
                    \item International Praxis of all stripes.
                \end{itemize}
            \item What is gonna happen to immigrants for real?
                poem???
                \\
                Are there any other student organizations organizing
                with the expectation of force?
                \begin{itemize}
                    \item Being met with force has many different
                        manifestations. Sometimes responding to
                        force with force is something student organizations
                        are not prepared for. Individual members
                        may be prepared.
                    \item University affiliated organizations are unable
                        to really fight bak with force.
                    \item Remember that school organizations can only
                        do so much "officially"
                    \item Many student organizers are frustrated with the
                        University. A lot of that frustration can be
                        put towards community building and counter
                        organizing.
                \end{itemize}
            \item What does it take for people to need change?
                \begin{itemize}
                    \item Collective thresholds are produced.
                    \item Ability to tolerate is produced.
                    \item Why can we just talk about Marxism and Communism
                        and the regents don't care?
                    \item Theory and not practice?
                    \item Not about the content but the form\\
                        As long as we are comfortable sitting here,
                        turning things in, and getting a grade we are
                        still being conditioned for capitalism.
                    \item Being wrong is okay, all it means is we need
                        a new practice, and new theory.
                \end{itemize}
                \pagebreak
            \item Resource
                \begin{mdframed}
                    Florence Project, provides free legal and social
                    services for immigrants facing deportation. Looking
                    for donations, anything is helpful.
                \end{mdframed}
        \end{itemize}
\end{description}



\end{document}
