\documentclass{report}
\usepackage[tmargin=2cm, rmargin=1in, lmargin=1in,margin=0.85in,bmargin=2cm,footskip=.2in]{geometry}
\usepackage{amsmath,amsfonts,amsthm,amssymb,mathtools}
\usepackage{enumitem}
\usepackage[]{mdframed}
\usepackage{tikz}

\title{\Huge{CRES 10}\\Discussion 4 Notes}
\author{\huge{Elijah Hantman}}
\date{}

\begin{document}
\maketitle
\newpage

\begin{description}
    \item Some extra thoughts 
        \begin{mdframed}
            The Taos trials resemble the trial
            of the Central Park Five. A trial that
            in retrospect looks like a sham trial to hide
            the true goal of silencing and suppressing.
        \end{mdframed}
        \begin{mdframed}
            The trial also makes me think that while being
            a citizen is a prerequisite for being considered
            by a Liberal government, citizenship also grants
            the government power over you whether consensual
            or coerced.
        \end{mdframed}
    \item Mexican-American War Prior
        \begin{itemize}
            \item A thing that happened
            \item Minimized and framed as the Almo
                not particularly in depth and
                overly focused on singular military
                victories and defeats.
            \item Framed as fighting for the sovereignty
                of Texas
            \item Not covered until college. In a Latin
                History class the war was framed in
                reference to who became president and who
                gained glory.
        \end{itemize}

    \item What is the Author doing?
        \begin{itemize}
            \item Reframe using colonialism as a lens
            \item Understand the US as an invading force
            \item Shows how the Mexican-American war was
                a breakthrough in imperialism
        \end{itemize}
    \item Why use Race as a lens?
        \begin{itemize}
            \item Larger foreign population in the US,
                Irish and German are seen as not
                the same as Americans. 
            \item Racialization was used as an Othering tool.
                The goal is to shift the focus to Mexicans
                as Others to incorporate German and Irish
                immigrants.
            \item Mexican is put in opposition to Whiteness.
            \item News demonizes Mexicans as foriegners.
        \end{itemize}
    \item How does she build her arguement?
        \begin{enumerate}
            \item She starts with a story she will return to
                later.
                \begin{itemize}
                    \item She explains the history of how the
                        story she started with will come about.
                    \item brutal story parallels the brutality
                        of the events she wishes to discuss.
                \end{itemize}
            \item IDK man the question is rambling
                \begin{itemize}
                    \item drawing of lines problematize
                        people
                    \item There are already people living on
                        the land we want to live on,
                        so the people already living there
                        become a problem
                \end{itemize}
            \item literally I'm lost 
        \end{enumerate}
\end{description}


\end{document}

