\documentclass{report}
\usepackage[tmargin=2cm, rmargin=1in, lmargin=1in,margin=0.85in,bmargin=2cm,footskip=.2in]{geometry}
\usepackage{amsmath,amsfonts,amsthm,amssymb,mathtools}
\usepackage{enumitem}
\usepackage[]{mdframed}
\usepackage{tikz}
\usepackage{minibox}
\renewcommand{\familydefault}{\sfdefault}

\title{\Huge{Math 181}}
\author{\huge{Elijah Hantman}}
\date{}

\begin{document}
\maketitle
\newpage

\begin{description}
    \item {\large EJ Edmunds Cont.}  
        \begin{mdframed}
            \begin{enumerate}
                \item E\'cole polytechnique
                \item 1875 Back in New Orleans
                    \begin{center}
                        \minibox[frame]{
                            No real info\\
                            His personal letters\\
                            and notes are not\\
                            avalible
                        }
                    \end{center}
                    \begin{mdframed}
                        Super Weird, New Orleans just
                        came out of Martial Law and is
                        a massive mess.

                        Not to mention that if he stayed in
                        France he would have been set up for
                        life.

                        Lots of violence both racist and
                        political.

                        For an educated well off black man,
                        he is in a good position to take
                        political leadership. Most freed
                        slaves could not read and had little
                        to no experience with politics.

                        Quickly manages to get a good position
                        in education. The Republican Party
                        at the time was investing highly into
                        education.
                    \end{mdframed}
                    \begin{mdframed}
                        Edmund first gets a job at
                        Sumor School which was a new,
                        all black school.
                    \end{mdframed}
                    \begin{mdframed}
                        Next Edmund ends up at Boys Central
                        H.S. which was an established
                        elite white school.

                        First day he comes to teach the students
                        leave in protest.
                    \end{mdframed}
                \item 1877 Edmund is removed from his teaching
                    position.
                    \begin{mdframed}
                        Massive election scandal, both parties
                        were engaging in voter fraud and
                        intimidation. Both parties disputed
                        the election and armed paramilitary
                        groups attempt to start their
                        own government. The President
                        sends in federal forces to quell the
                        peace, before getting cold feet and
                        pulling out.

                        The Conservative Democrats had a bigger
                        paramilitary force and so seized power.
                        They removed Republican and Black officals
                        from office.
                    \end{mdframed}
                    \begin{mdframed}
                        Teaches at Colord H.S.

                        Peabody Normal School for Coloreds
                    \end{mdframed}
                    \begin{mdframed}
                        Schools ended up being segregated.
                        Normal schools was like a trade school
                        for teachers. It was less prestigous
                        than a college but was still
                        higher education.
                    \end{mdframed}
                \item 1878 Edmunds Develops serious health
                    problems (Yellow Fever).
                    \begin{mdframed}
                        Serious Epidemic which starts
                        in port cities like New Orleans.
                        Yellow Fever was rampant but
                        it is unclear what Edmunds' health
                        problem is.
                    \end{mdframed}
                \item 1880 Edmunds returns to Paris
                    \begin{mdframed}
                        Even before he returns to Paris he
                        is very prolific and outputs a
                        significant amount of mathematics.
                    \end{mdframed}
                \item 1881 Returns to New Orleans
                    \begin{mdframed}
                        Teaches at Southern University,
                        which is a historically black
                        university. Modern name is Southern
                        A\&M.
                    \end{mdframed}
                \item 1882 Moves to town of St. Joseph
                    \begin{mdframed}
                        Small town in Louisiana.
                        On the border of Louisiana and
                        Mississipi.
                    \end{mdframed}
                    \begin{mdframed}
                        Gets hospitalized, and is
                        bedridden for the rest of his life.
                    \end{mdframed}
                \item 1887 Edmunds Passes on.
            \end{enumerate}
        \end{mdframed}
    \item {\large Takeaways}
        \begin{itemize}
            \item Both Edmunds and Euler focused on mathematics
                but their lives were also shaped by political
                forces.
            \item Euler and Edmunds could only do mathematics
                because of their favorable situations. 
                Euler had a better situation than Edmunds
                but both required specific circumstances.
        \end{itemize}
    \item {\large Remanants}
        \begin{mdframed}
            Not only is Euler more important to the field
            of mathematics, but also after Repubilcans
            lose political power in the South much was done
            to undo and prevent them from ever regaining power.
        \end{mdframed}
        \begin{mdframed}
            Birth of a Nation, super racist, super confederate,
            famous for being a landmark film unfortunate.
            An example of Conservatives in the South trying
            to create a narrative which serves them politically.
            And one of those things they did was erase the
            contributions of figures like Edmunds.
        \end{mdframed}
        \begin{mdframed}
            Past events are immutable, but history is always
            being rewritten, with better methodology, and more
            research.
        \end{mdframed}

        \begin{center}
            \minibox[frame]{
                Derek J. Struik was a mathematician\\
                who contributed to differential\\
                geometry. He also gained an interest\\
                in history and made great contributions\\
                there as well. He was also a communist\\
                and was criminally charged for trying\\
                to overthrow the state.
            }
        \end{center}
        \begin{mdframed}
            How do we know what Euler did?
            \begin{mdframed}
                His work was preserved since he worked
                at a major university. His work was
                disseminated widely and is now in
                many European University libraries.
            \end{mdframed}
            \begin{mdframed}
                This made it easy to study his work,
                however, it is also hard because he produced
                so much mathematical material that it is impossible
                to fully trace his influence. It is also difficult
                to contribute because Euler is so well studied,
                so new contributions to Euler's history are few and
                far between.
            \end{mdframed}
        \end{mdframed}
    \item {\large EJ Edmunds Work}
        \begin{mdframed}
            
        \end{mdframed}
\end{description}
\end{document}
