\documentclass{report}
\usepackage[tmargin=2cm, rmargin=1in, lmargin=1in,margin=0.85in,bmargin=2cm,footskip=.2in]{geometry}
\usepackage{amsmath,amsfonts,amsthm,amssymb,mathtools}
\usepackage{enumitem}
\usepackage[]{mdframed}
\usepackage{tikz}
\usepackage{minibox}
\renewcommand{\familydefault}{\sfdefault}

\title{\Huge{Art 25}}
\author{\huge{Elijah Hantman}}
\date{}

\begin{document}
\maketitle
\newpage

\begin{description}
    \item {\large Society of the Spectacle}  
        \begin{mdframed}
            \begin{itemize}
                \item Games are considered to be separate from
                    life, that is an illusion.\\
                    Games are a part of life, and their ability
                    to impact us is only possible because
                    the relationship goes two ways.
                \item Wartime propaganda
                    \begin{itemize}
                        \item He is talking about SS soldiers
                            being depicted as a evil baboon,
                            I think it is actually supposed to
                            be a Japanese soldier.
                        \item I think he mixed up the anti-Nazi
                            and ant-Japanese propaganda.
                    \end{itemize}
                \item Post War Propaganda
                    \begin{itemize}
                        \item Family Unit
                        \item Christianity
                        \item Whiteness
                        \item Informationals, the way society is,
                            is how society was, and how society
                            will be. Society is formulaic.
                    \end{itemize}
                \item Firefighters
                    \begin{itemize}
                        \item Most firefighters are prisoners
                        \item Many are POC
                        \item FPS but you save people
                    \end{itemize}
                \item Cops
                    \begin{itemize}
                        \item Thin blue line
                        \item Masculinity
                        \item White
                        \item Violence
                        \item FPS cops are always presented as correct
                        \item Don't think about it
                        \item It's usually men
                    \end{itemize}
                \item My reality is built from my experience,
                    it is experience weighted by history,
                    and it is worth it to critically examine
                    both my history and my experience.

                    \begin{center}
                        \minibox[frame] {
                            OMG I hate how often he\\
                            uses "Operating System"\\
                            as a phrase. Like it doesn't\\
                            make sense, just use anything\\
                            else, please I beg.
                        }
                    \end{center}
                \item The goal of "Spectacle" as a theoretical
                    framework:
                    \begin{mdframed}
                        To Reinforce, using representational
                        modeling and behavioral modeling, the
                        subconscious ways that the powerful
                        want you to do, make, say, think to
                        uphold their power.
                    \end{mdframed}
                    \begin{center}
                        \minibox[frame] {
                            I kinda disagree with the prof\\
                            He is asserting that games are\\
                            not aware of their artistic or\\
                            political abilities. I think he\\
                            is imagining games as only\\
                            the triple A or other art as only\\
                            the indie or fine.\\
                            Students recreate what they know\\
                            as a gateway into what they do\\
                            not know. The more money behind\\
                            a project the safer and less pointed\\
                            it is. Its true in movies, paintings,\\
                            music, etc.\\
                            Some examples of politically thoughtful\\
                            games include, Umurangi Generation,\\
                            Star Fetchers, and even missle command\\
                            all the way back in the 1980s.\\
                            Artful games range from Manifold Garden\\
                            to Return of the Obra Dinn, Cosmo D,\\
                            Hyperbolica, 4D Golf, Fractal Racer,\\
                            Fractal Block World, etc.
                        }
                    \end{center}
            \end{itemize}
        \end{mdframed}
    \item Value Capture
        \begin{mdframed}
            \begin{itemize}
                \item Games: Agency as Art
                \item C. Thi Nguyen
                \item Worry about gamefication etc.
                \item Value Capture
                    \begin{itemize}
                        \item Values are rich and subtle
                        \item Environment presents simplified and
                            quantized versions of these values
                        \item Simplified values begin to dominate
                            the agent's reasoning.
                    \end{itemize}
                    \begin{mdframed}
                        An example is money. My desires are rich
                        and subtle, I want good food, I want good
                        company, security, etc. Money is required
                        for almost all of these, and it can be easy
                        to start thinking in terms of money rather
                        than in terms of what I want money for.
                    \end{mdframed}
                \item Games
                    \begin{itemize}
                        \item Achievement vs Striving Play
                            \begin{mdframed}
                                Achievements are about winning,
                                and winning only.\\
                                Striving play is about the process
                                of victory.

                                \vspace{10pt}

                                Climbing is striving,
                                speedrunning is striving,
                                grinding is achievement,
                                etc.
                            \end{mdframed}
                        \item We can easily adopt temporary value
                            systems
                        \item We gain value clarity
                            \begin{mdframed}
                                We get a space where choices are
                                easier than real life and we can
                                simply enjoy the process of acting
                                towards a goal.
                            \end{mdframed}
                    \end{itemize}
                \item Non-Games
                    \begin{mdframed}
                        It makes it difficult to put down the
                        temporary value systems.
                    \end{mdframed}
            \end{itemize} 
        \end{mdframed}
\end{description}


\end{document}
