\documentclass{report}
\usepackage[tmargin=2cm, rmargin=1in, lmargin=1in,margin=0.85in,bmargin=2cm,footskip=.2in]{geometry}
\usepackage{amsmath,amsfonts,amsthm,amssymb,mathtools}
\usepackage{enumitem}
\usepackage[]{mdframed}
\usepackage{tikz}

\title{\Huge{CRES 10}\\Discussion 1}
\author{\huge{Elijah Hantman}}
\date{}

\begin{document}
\maketitle
\newpage

{\large Intros}
\begin{enumerate}
    \item Lalu is the TA, film and digital media phd candidate
        from Turkey. \textit{they/them}

        Focused on Sex Work, Trans communities, intersection between
        various groups and film.

        Attempt safe space, but like, be ready
\end{enumerate}

{\large Discussion Notes}
\begin{enumerate}
    \item What is a safe space?
        \begin{description}
            \item mindful of tone
            \item Room for disagreement
            \item room for discomfort with respecting boundaries
            \item limits on what is practical, institutions
                impose limits on whether people even can feel
                safe.

        \end{description}
    \item Readings
        \begin{description}
            \item Page 16 "Race is the child of Racism
                not the father"

                \begin{enumerate}
                    \item Race is used to divide,
                        it is not a feature of the
                        natural world. It is a purely
                        negative attribute, meant to
                        denegrate the outsiders.
                    \item Psych studies, no geneological
                        difference besides skin tone.
                        Health, and other physiological
                        metrics are the same.

                        Racial groups have no scientific basis.

                    \item Historically slavery was economic
                        and racism was the justification
                        that allowed it to be morally
                        acceptable.

                        Racism is a tool to other, not an
                        enevitability.

                        Black people are reduced to flesh
                        automatons, labor and value to be
                        extracted.
                    \item Consumerism and greed is the father
                        of racism. Capitalism creates race
                        and through race it maintains an
                        underclass.
                    \item Historical context. Race and Racism
                        starting in America. Nathaniel
                        Bacon rebellion, black slaves and 
                        white indentured servants rebelled.

                        Race was then used as a tool to prevent
                        Black and White workers from joining
                        together on the base of class.
                    \item Why is Racism the Father?

                        What came first??
                        Why not the mother?

                    \item Term Mother is more caring
                        nurturing, natural.

                        Father dominating, patriarchy.
                \end{enumerate}
            \item End of Part 1 Pg 80.
                "You have to make your peace with the Chaos
                you cannot lie"

                \begin{enumerate}
                    \item Interesting, opposite to another
                        good essay.

                        Other essay claims that there is no
                        revolution without madness, you cannot
                        make peace with injustice.

                        Perhaps both are true?

                    \item Expectation that mostly White people
                        have, that POC are complacaent or
                        resigned to their circumstances.

                        For survival sake you have to play the
                        game, you have to bend the knee. But
                        don't forget that this is wrong and
                        that things can be different.

                    \item Radical acceptance but not passivity
                        It is what it is, things can be
                        different but you are alive now.

                        "Our revenge will be the laughter of
                        our children"

                    \item Revolutionary optimism
                        
                        Attending university
                        Do what you have to do
                        Make the world better in ways you can.

                    \item The lie is that if you reach high enough
                        you will be indistinguishable from being
                        White.

                        There is no escape from Race as long as you live
                        in society. You must make your peace with that.

                    \item Something people have to learn growing up.

                        Black Excellence and Anti-Black beauty
                        standards.

                        It is a losing game, you have to accept the
                        parts of yourself that are not wrong.

                    \item Over policing

                        policing the self comes from our parents.
                        Parents who reproduce the abuses of the
                        system in order to innoculate children
                        against the cruelty of the world.
                \end{enumerate}

            \item "It is a profound question because America
                understands itself as God's handiwork, but
                the black body is the clearest evidence that
                America is the work of Man"

                \begin{enumerate}
                    \item Race is the father of racism

                        This quote emphasized the man-made
                        nature of racism.

                        Race did not exist until it could
                        serve a purpose in the machinery
                        of imperialism.

                        Essentialist stories about race
                        serve the absolution of cruel
                        systems.
                    \item The treatment of African Americans
                        is one of the clearest demonstrations
                        of the failure of America as an
                        endeavor.

                        We are often told stories of a
                        perfect America, or at least an
                        America which is as close to perfect
                        as is reasonable.

                    \item Basis of slavery was religion.
                        Christians used scripture to explain
                        racism and slavery. God willed slavery
                        god desires slavery, god cursed
                        the slaves.

                        America is deeply influenced by christianity.
                        Christianity is apparent in every level
                        of American government and laws.

                        A lot of the early colonies were religious
                        havens.

                        Manifest destiny was inherited throughout
                        colonial powers past and present.

                    \item Throughout all American history, Religion
                        has been a massive justification for racism
                        and bigotry.

                        We still use a 2,000 year old book to justify
                        legal and moral decisions.
                \end{enumerate}
        \end{description}
\end{enumerate}



\end{document}
