\documentclass{report}
\usepackage[tmargin=2cm, rmargin=1in, lmargin=1in,margin=0.85in,bmargin=2cm,footskip=.2in]{geometry}
\usepackage{amsmath,amsfonts,amsthm,amssymb,mathtools}
\usepackage{enumitem}
\usepackage[]{mdframed}
\usepackage{tikz}
\usepackage{minibox}

\title{\Huge{CRES 10}\\Day 8 Notes}
\author{\huge{Elijah Hantman}}
\date{}

\begin{document}
\maketitle
\newpage

\begin{description}
    \item Final Word on Liberalism
        \begin{mdframed}
            Liberalism had both consequences and
            benefits. Freedom, democracy, etc. all the
            things Liberalism can't let us forget it
            stands for. It also has a focus on capitalism
            and nationhood which both hides and incentivises
            abuses against non-citizens and the poor. Liberalism
            also fails when it comes to understanding
            and critiquing itself.

            Particular notion of what a person is, particular
            views on what a person is entitled to. People are
            defined by contrast to non persons.
        \end{mdframed}
        \begin{mdframed}
            Aziz Rana Critique of American Liberalism
            \begin{enumerate}
                \item Transformas Historical experiences of oppression
                    into abberrational features of American life. Makes
                    oppression out to be the exeception rather the rule.
                \item American founding is presented as an anti-imperial
                    act rather than the start of a new imperial power.

                \item Gives a context in which reform is the default
                    and only reasonable action rather than anything
                    more extensive.
            \end{enumerate}

            When first generation students were telling their story
            for graduate programs, they started with coming to the
            US for a better life. They knew that the US is the reason
            their lives in their home countries became worse.
            The Story of Immigrants to the US is one that institutions
            expect, one of gratitude towards the US and gratefulness
            for the US.

            Legitimacy is bought via the espousing of a narrative
            which is flattering to America. America is a force
            for good and the odd abuse or infraction is an exception
            not the rule.
        \end{mdframed}
    \item {\large Franchise vs Settler Colonialism}
        \begin{mdframed}
            Settler colonialism has colonizers stay.
            Colonizers are often fleeing or seeking new
            opportunities. The goal is to replace
            the natives not mere to extract resources.

            Settler colonialism creates a crisis, where
            later generations of settlers have no where
            else to go, and no other home except one built
            on blood and violence.

            Built on the elimination and replacement of
            natives. Elimination is more than just violence
            but also erasure, and indoctrination. The goal is
            not just to replace natives physically, but culturally
            and socially.

            If the natives are not killed they must be made
            like the settlers. Or into something that can be
            safely subsumed by settler society.
        \end{mdframed}
        \begin{mdframed}
            Franchise colonialism is purely about extracting
            resources. Only the upper class administration
            is imported, and they do not replace
            the natives, but extract their labor, resources,
            land, etc.
        \end{mdframed}
        \begin{mdframed}
            Critique is not necessarily opposed. One can
            acknowledge flaws, then throw up their hands
            and ignore them. You can hate something and
            not truly threaten it. Criticism becomes a
            politics of recognition and is therefore
            assimilated back into these structures.
        \end{mdframed}
    \item {\large Structural vs Sudden Genocide}
        \begin{mdframed}
            What is the difference between law and Justice?
        \end{mdframed}
        \pagebreak
    \item {\large UN definition}
        \begin{mdframed}
            Genocide as a term comes from after WWII, 
            genocide was established to be acts committed
            with intent to destroy in whole or in part, a
            national, ethnic, racial, or religious group.

        \begin{center}
            \minibox[frame]{
                sidenote: the US only ratified when\\
                a clause exempted the US from proscecution\\
                without the consent of the US.
            }
        \end{center}

        Much of the UN definition covered actions the US was
        actively or had been actively engaged in.
    \end{mdframed}
    \item {\large International Law}
        \begin{mdframed}
            International law is often seen as a way of
            contesting entrenched power and abuse. However
            it is also a means of enforcing and defending
            aforementioned power and abuses.
        \end{mdframed}
        \begin{mdframed}
            Sudden genocides are about mass killings, they
            involve the culmination of long term oppression
            and stigma. They are fast and short.
        \end{mdframed}
        \begin{mdframed}
            Structural genocide is about long term
            removal. Mass killings and sudden genocides can
            be small parts but are not the whole. It is
            a genocide which is self-legitimized, it is
            everything but violence. It is changing the
            world such that a certain type of person becomes
            unviable.

            Oppression is not invincible. It can be defeated,
            if rarely. To fight and kill in resistance
            to oppression is a good thing, victimhood isn't
            something special or good beyond the fact that
            the one doing the oppressing is bad.
        \end{mdframed}
    \item {\large}
\end{description}

\end{document}
