\documentclass{report}
\usepackage[tmargin=2cm, rmargin=1in, lmargin=1in,margin=0.85in,bmargin=2cm,footskip=.2in]{geometry}
\usepackage{amsmath,amsfonts,amsthm,amssymb,mathtools}
\usepackage{enumitem}
\usepackage[]{mdframed}
\usepackage{tikz}
\usepackage{minibox}
\renewcommand{\familydefault}{\sfdefault}

\title{\Huge{Math 181}}
\author{\huge{Elijah Hantman}}
\date{}

\begin{document}
\maketitle
\newpage

\begin{description}
    \item {\large History of Mathematics Approaches}
        \begin{itemize}
            \item History via Biography
                \begin{mdframed}
                   For example the Documentry on Andrew Wiles,
                   and Fermat.

                   Who have we heard of?
                   \begin{itemize}
                       \item Andrew Wiles
                       \item Fermat
                       \item Kumming
                       \item Sophie G.
                       \item etc.
                   \end{itemize}

                   Who should we know of?
                   \begin{itemize}
                       \item John Nash
                           \begin{mdframed}
                               Known for game theory, but best
                               well known for tragically being
                               dehibilitated by Schizophrenia.

                               \vspace{10pt}

                               John Nash in his biography was a
                               bisexual man, and was denied
                               some jobs for his sexuality.
                           \end{mdframed}
                       \item Evariste Galois
                           \begin{mdframed}
                               Known for Galois theory, which
                               is a theory for studying polynomial
                               equations. Famously proved the zero-roots
                               of a quintic equation cannot be written
                               as a combination of addition, subtraction,
                               division, multiplication, and roots.

                               \vspace{10pt}

                               Died around 23 from a duel. Dramatic
                               life story. Lived during the time of the
                               French revolution, and was interested
                               in revolutionary politics.
                           \end{mdframed}
                       \item Srinivasa Ramanujan
                           \begin{mdframed}
                               Ramanujan Conjecture won a fields
                               medal when solved. 
                               \vspace{10pt}

                               Grew up in India under British rule.
                               Inspired to do mathematics and ended
                               up unable to continue in University as
                               a student. Wrote up some mathematical ideas
                               he had and sent it to some British
                               mathematicians and caught the attention
                               of leading mathematician Hardy.
                               Hardy recognized Ramanujan was a genius,
                               and brought him to England to work with
                               him. Ramanujan eventually became ill and
                               died before 30.

                               \vspace{10pt}

                               Was a famous Indian Mathematician and
                               had a very dramatic and tragically short
                               life story.
                           \end{mdframed}
                       \item Sophie Germain (I mentioned her earlier)
                           \begin{mdframed}
                               She worked on Fermat's Last Theorem.
                               She was a female mathematician working
                               at a time women were denied education
                               and power in public life.
                           \end{mdframed}
                       \item Emmy Noether
                           \begin{mdframed}
                               She made many important contributions
                               to abstract algebra. Noetherian ring,
                               Noether's theorem in physics.

                               Both father and brother were talented
                               mathematicians, made contributions to
                               Algebraic geometry, etc.

                               \vspace{10pt}

                               She was also a Jewish mathematician during
                               the rise of Nazi Germany. She ended up moving
                               to the US to flee the Nazis. She was also
                               in a similar situation to Sophie Germain,
                               many women were still heavily discouraged
                               from studying higher education.
                           \end{mdframed}
                           \pagebreak
                       \item David Hilbert
                           \begin{mdframed}
                               Same university as Noether, posed famous
                               problems which shaped mathematics research.
                               Somewhat of a polymath with results in many
                               disciplines.
                           \end{mdframed}
                       \item George Cantor
                           \begin{mdframed}
                               Major contributions to set theory. Multiple
                               types of infinities, no bijections between
                               reals and rationals.
                           \end{mdframed}
                           \begin{center}
                               \minibox[frame]{
                                   Many of these people are german,\\
                                   why is that? What was going on in\\
                                   Germany to spur such a culture?
                               }
                           \end{center}
                       \item Alan Turing
                           \begin{mdframed}
                               Famously a homosexual mathematician
                               who was persecuted by the British
                               government. He was chemically sterilized
                               and his contributions were hidden for
                               many years.

                               \vspace{10pt}

                               Famously broke the Nazi Enigma code
                               during the second world war.

                               \vspace{10pt}

                               Also made many foundational contributions
                               to theoretical computer science, Turing
                               Machines, P and NP.

                               \vspace{10pt}

                               Contributions to mathematical biology.
                           \end{mdframed}
                       \item Ada Lovelace
                           \begin{mdframed}
                               Analytical machines, and general
                               computing. Considered by some to
                               be the first programmer.

                               \vspace{10pt}

                               Predates electronic solid state
                               computing. Also predates programming
                               languages as a concept.

                                \vspace{10pt}

                                Related to famous poet Byron.
                           \end{mdframed}
                           \begin{center}
                               \minibox[frame] {
                                   What differentiates fields?\\
                                   Early Computer Scientists were\\
                                   mathematicians. Early mathematicians\\
                                   were philosophers.
                               }
                           \end{center}
                       \item John von Neuman
                           \begin{mdframed}
                               Helped invent game theory,
                               one of the first programmers
                               (von Neuman architecture).

                               Many other contributions.
                           \end{mdframed}
                       \item John Conway
                           \begin{mdframed}
                               Automata, Monstrous Moonshine Conjecture,
                               etc.\\
                               Good speaker and teacher.
                           \end{mdframed}
                       \item Pythagorus
                       \item Archimedes
                       \item Euclid
                       \item Euler
                       \item Newton
                       \item Bernoulli
                   \end{itemize}
                \end{mdframed}
        \end{itemize}
    \pagebreak
    \item 
        Which people could we study in the history of
        Mathematics?
        \begin{mdframed}
            \begin{itemize}
                \item Professors of modern-ish universities 
                \item Amateur Mathematicians with Large Contributions
                    \begin{mdframed}
                        People like Fermat who was read by
                        professors and respected.
                    \end{mdframed}
                \item Layperson math
                    \begin{mdframed}
                        What was taught and who
                        was learning?
                    \end{mdframed}
                \item Lecturers and Math communicators?
                    \begin{mdframed}
                        Grant Sanderson\\
                        Berkand Polster
                    \end{mdframed}
                \item Commercial or Industrial math 
                    \begin{mdframed}
                        Investment\\
                        Engineering\\
                        NSA\\
                        Bell Labs\\
                        Microsoft, etc.
                    \end{mdframed}
                \item Public Intellectuals
                    \begin{mdframed}
                        Lagrange\\
                        Bertrand Russell\\
                        etc. 
                    \end{mdframed}
                \item Think tanks
                    \begin{mdframed}
                        OpenAI\\
                        Research Institutions
                    \end{mdframed}
                \item Multidisciplinary Math
                    \begin{mdframed}
                        Artists\\ 
                        Muscicians\\
                        Computer Scientists\\
                        Physicists
                    \end{mdframed}
            \end{itemize}
        \end{mdframed}
    \item Concluding
        \begin{mdframed}
            Thoughts on Mathematical Movie posters.
            \begin{itemize}
                \item A Beautiful Mind (John Nash)
                    \begin{itemize}
                        \item Sad
                        \item Smart Brain man
                        \item Individual
                        \item Personal over factual
                        \item Weird + exceptional
                        \item Big name actors with contracts
                        \item Mental health
                        \item Notable abscence of mathematics
                    \end{itemize}
                \item The Imitation Game (Alan Turing)
                    \begin{itemize}
                        \item Individual
                        \item Weird man
                        \item Big smarty brain
                        \item Lack of mathematics
                        \item similar framing to previous poster
                    \end{itemize}
                \item The Man Who Knew Infinity (Ramanujan)
                    \begin{itemize}
                        \item Not looking at viewer
                        \item white background
                        \item Two people (Hardy and Ramanujan)
                        \item Mathematics on the poster
                        \item Why is Good Will Hunting on the
                            poster lmao
                        \item First non-white man depicted so far,
                            only one where the main character
                            isn't alone.
                    \end{itemize}
                \item Hidden Figures
                    \begin{itemize}
                        \item Shot like action poster
                        \item Less emphasis on "extrodinary mind"
                        \item Full body shot
                        \item Setting in the background
                    \end{itemize}
            \end{itemize}
            How do people like those in Hidden Figures,
            become known? How do we build biographies?
            \begin{itemize}
                \item Federal documents
                \item Obituaries
                \item Papers and Mathematics
            \end{itemize}
        \end{mdframed}
\end{description}


\end{document}
