\documentclass{report}
\usepackage[tmargin=2cm, rmargin=1in, lmargin=1in,margin=0.85in,bmargin=2cm,footskip=.2in]{geometry}
\usepackage{amsmath,amsfonts,amsthm,amssymb,mathtools}
\usepackage{enumitem}
\usepackage[]{mdframed}
\usepackage{tikz}

\title{\Huge{CRES 10}\\Day 5 Notes}
\author{\huge{Elijah Hantman}}
\date{}

\begin{document}
\maketitle
\newpage

\begin{description}
    \item {\large Misc Announcements}
        
        Violating university policy can be treated as 
        an arrestable offense due to Ronald Reagan's
        time as California state governor.
    \item {\large John Locke}
        \begin{mdframed}
            \begin{itemize}
                \item
                    Property is the combination of labor
                    with land. He was an early proponent of
                    freedom being about owning property.

                    Knowledge is not innate, a proponent of
                    the blank slate model of human learning.

                \item
                    Improvement of the land.

                \item
                    Disagreed with Thomas Hobbes

                \item 
                    Human rights come from property rights,
                    all humans are the property of god, and
                    to violate the another is an affront to god.
            \end{itemize}

            How does John Locke's whiteness affect his philosophy?\\
            What is the relationship between freedom, property, and race?
        \end{mdframed}
    \item {\large Recap}
        \begin{itemize}
            \item Racism is both the outcome and a process itself
            \item Racism is the intermediate, it is a tool which is produced
                and used to create outcomes

            \item One thing Racism does is flatten the diversity of humanity
                into simple groups

            \item The process of flattening people into a single category
                requires both physical and cultural violence.
        \end{itemize}
    \item {\large Weird Q\&A}
        \begin{itemize}
            \item When I talk to my friends about this class,
                they say that the perspective it provides is a
                liberal one. Is that the same Liberalism you're
                talking about?

                \vspace{10}

                No! This class offers perspectives that are largely
                critical of Liberalism. But the liberalism it critiques
                is not the same as American Liberalism.

                In the US, Liberal has been associated with the Democrat
                Party, but historically in political philosophy, liberalism
                applies to both Democrats and Republicans.

            \item Liberalism is often thought of as oppositional to conservatism,
                but liberalism encompasses both?

                \vspace{10}

                Liberalism is a supremacist ideology. It thinks of itself as
                the most free. It places a unique value on individual freedom
                and individualism. Liberalism therefore has difficulty
                critiquing itself. Why would a philosophy obsessed with freedom
                produce so many kinds of unfreedom. Why would a philosophy
                obsessed with justice produce so much injustice.

                One example is the nonsensical explanations for 9/11. A Liberal
                government said that they just hated us and our freedom, it
                cannot look at itself and understand 9/11 as a response to
                US extraction, exploitation, and violence.

            \item One example of Liberalisms other faults is the focus on individualism.
                When talking about climate change, liberals will often focus on individual
                actions rather than systemic or group actions.

                In addition, Liberalism is inextricable from capitalism and so thoughts
                are filtered through individualist and capitalist lenses to present
                market solutions like Medicare, rather than more systemic solutions
                like the NHS.

            \item Liberal stories can't help but make itself the ideology of the
                good guys. Capitalists are good individuals except for the few bad
                apples who cheated the system, and the the current system is
                good and there are only a few tweaks to fix everything.

            \item What do progressive and libertarian mean in this context?

                \vspace{10}

                Libertarian ideology is similar to classical liberalism. Progressiveism
                usually means that we need good institutions to save liberalism from
                itself.

            \item Is liberalism seperable from capitalism?

                \vspace{10}

                Capitalism can operate outside of liberalism, in authoritarian or
                non-liberal spaces. Liberalism may be confined to capitalism
                due to its fetishization of property.

            \item Okay, Liberalism, back in the day, but isn't the solution just to
                commit to freedom for everyone?

                \vspace{10}

                Does unfreedom only happen in the past? Does liberalism primarily
                produce freedom, or does it produce unfreedom by design? Is poverty
                unfreedom, what about prisons, what about the massive military? What
                about all the ways liberalism continues to support and employ colonialist
                tactics.

            \item I think I'm still struggling with what liberalism is?

                \vspace{10}

                Liberalism understands freedom as the right to privately own property.
                Liberalism views rights as property, and the role of a state is to
                enforce property rights.

                The thing that makes people equal is that every human can individually
                own property. 

            \item Why would a non-slave owner support slavery?

                The existence of slavery pushes the price of all
                goods down. It allows space for the non-slaves to gain access to goods
                which were otherwise impractical to obtain. It produces enough
                labor to allow for global capitalism.

                A definition of freedom that is based off of not being
                in bondage.

                A product of identity being sold to allow for the psychological and
                social uplift of Whites.

            \item Okay, isn't the solution just to make everyone free?

                Given the history, why should we trust liberalism? What kinds
                of freedom does liberalism even produce, is it something that
                is the "best"? 

            \item Liberalism sees freedom as property, what does that have to do
                with race?

                Private ownership of land is one of the most important parts of
                liberal freedom, and settler colonialism is inextricable from
                US land ownership. The seizure of the commons for private
                ownership is a racializing process.

                Land and common property is seized and the previous inhabitants are
                racialized in order to establish the private property system.

                The crux of settler colonialism is about establishing governance,
                and to establish a private property system you need to establish
                a system of governance which is friendly to private property.

                \vspace{10}

                Settler governance allows for the accumulation of wealth. Wealth
                is the economic power and social power which is greater than
                that of what an individual can produce. Wealth is about many
                generations of gaining more than you could produce, and one
                of the best ways to do that is to enslave someone and extract
                their labor and value.

                Under the liberal framework, even a freed slave will be
                disadvantaged compared to their masters. Race is produced via
                the liberal framework which solidifies wealth differences
                through the freedom that wealth grants to exert power over
                others.

        \end{itemize}
    \item {\large }
\end{description}


\end{document}
