\documentclass{report}
\usepackage[tmargin=2cm, rmargin=1in, lmargin=1in,margin=0.85in,bmargin=2cm,footskip=.2in]{geometry}
\usepackage{amsmath,amsfonts,amsthm,amssymb,mathtools}
\usepackage{enumitem}
\usepackage[]{mdframed}
\usepackage{tikz}
\usepackage{minibox}

\title{\Huge{CRES 10}\\Day 4 Notes}
\author{\huge{Elijah Hantman}}
\date{}

\begin{document}
\maketitle
\newpage

\begin{mdframed}
    {\LARGE Agenda}
    \begin{itemize}
        \item Word on last year
        \item Content Warnings
        \item Recap: Definitions, key terms, distinctions
        \item Liberal Theories of Racism
        \item A Weird Q\&A
    \end{itemize}
\end{mdframed}

\begin{description}
    \item {\Large Words on Last Year} 
        
        \begin{center}
            \minibox[frame]{
                Complexity is not a virtue
                in itself.\\

                What does simplicity make avalible\\
                in a way complexity does not.\\

                What does complexity cover that\\
                simplicity does not.\\

                Granularity is not always good.
            }
        \end{center}

        Israel Palestine is often avoided through
        mentions of complexity. Humility is important,
        the urge to learn more is good. Simplicity can allow
        for clarity. Low granularity, chunking, can be useful.
        The Reading shows this, the framing of settler colonialism
        has high granularity, but the author dips out of that
        complexity to show how there are still broad simple
        trends.
        South Africa is a good example, it is a settler colonial
        state. The history of South Africa is long and complicated
        and there are numerous influenes, however at its base
        it is a colonial state.
        Australia is another example, it is not the same as South
        Africa, but it still came about and falls under the Umbrella
        of Settler Colonialism.
        Israel is a settler colonial state. 

        To completely understand Israel is a task which is gargantuan,
        however to chunk Israel, and see broad Ideological influences,
        material origins, and economic incentives.

        People are not oppressed absolutely, groups can move in and
        out of various systems of oppression and extraction.

        The settler colonial framework is useful because of how it
        allows for a broad enough understanding of history to avoid
        amnesia. It allows for the ideological movements and the
        slow demographic shifts.

        \vspace{10}

        The War in Gaza is dependent on weapons. Weapons come from
        internal Israeli tech and military industries. A lot of it
        comes from US alliship, where they are provided Billions of 
        dollars for purchasing weapons. War is a powerful tool for
        racialization and othering.

        \begin{center}
            \minibox[frame]{
                Technically international law
                obligatetes the US to stop sending weapons
                to Israel.\\

                However the US does not care about International law
                beyond its ability to write the laws.
            }
        \end{center}

        \pagebreak
        \begin{mdframed}
            {\Large Question}

            Can a Jewish state dedicated to the wellbeing of Jews ever exist in a
            non-colonial context?

            Responses
            \begin{itemize}

                \item The professor thinks it is possible, and that Israel is the result
                    of a failure of the UN to make Europe a safe place to be Jewish.

                \item Jewish Anti-Zionism is as old as Zionism, and the idea of Israel
                    as a safe place for Jews is not necessarily true.

                \item The idea of a dedicated state for a given racial/ethnic group is 
                    an idea based on the same foundation of anti-semitism.

                \item Israeli citizens are vocally protesting the ongoing genocide. The
                    government is not the same as the governed.

                \item Distinction between states and peoples, the citizens do not directly
                    control the state, even in "democracies"

                \item Protests in Israel, not necessarily against genocide. Primarily
                    about making a deal to release hostages. They are not necessarily
                    anti-war.

                \item Israel tries to conflate itself with Judaism. It is a flattening of
                    identiy akin to Whiteness.

                \item October 7th in relation to Jewishness. Zionism is a particular
                    nationalist, ideology and movement that arose in response to the
                    systematic oppression of Jews in Europe. It insists that the only
                    way for Jews to be safe and free is to establish a strong, militarily
                    powerful nation. The goal is to leave the "diaspora" and return to
                    prominance.
            \end{itemize}
        \end{mdframed}

    \item Content Warnings
        \begin{itemize}
            \item Acknowledgement that materials are impactful and can cause harm or distress
                to those reading or experiencing them.

            \item They can alert us to important questions around access. If a person who
                has suffered harm knows in advance they can be more mentally prepared
                and engaged.

            \item Can present issues. The goal of the class is to carefully expose and
                pick apart these topics, not sheild ourselves or each other from them.

            \item Discomfort in reasonable, controlled amounts is useful and important.
                The point of critical theory is to poke at the things which we might
                otherwise not think about.

            \item Not the same as continuing trauma.

            \item Complexity is useful for adding nuance, for navigating unclear
                or seemingly parodoxical issues. Complexity is a resource we try
                to fine tune to get the best, and most clear understanding of the
                issues in the world.
        \end{itemize}

    \item Passive Voice

        Passive voice is used to make things seem normal, natural.
        For example, \textit{Guns, Germs, and Steel} frame the Indigenous
        genocide in the Americas as the result of disease and natural processes.

        Nuanced definitions of racism seek to remove the passivity and neutrality
        from racism. Racism is not a feature of the universe and is, in fact, something
        we do to each other.
    
    \item  Key terms
        \begin{itemize}
            \item Racialization

                The construction and production of racial distinctions.
            \item Construction

                The outputs of human creative processes. Both physical and
                conceptual.
            \item Production

                The process of human creation. The gathering of raw materials
                the fabrication, the gathering of labor, organization, the
                planning, and desires behind the production process.
        \end{itemize}

        \begin{center}
            \begin{mdframed}
                The ideas in our head inform the way we build our world.
                Our world then shapes how we are forced to interact with
                each other.

                The things in our head are inscribed on reality through how
                we organize ourselves.
            \end{mdframed}
        \end{center}

        Racism both constructs new distinctions but also collapses large
        diverse groups into a single category. It is a forcible reframing
        of the position of people in society, White people are reframed
        as white and superior, Black people are reframed as cultureless
        slaves.

\end{description}


\end{document}
